\documentclass{article}      	% Style of the document                     

%% CONFIG

\IfFileExists{./.config.tex}{
  \input{.config}
}
{
  \def\isanonymous{1}
  \def\isfullversion{1}
  \def\buildexternal{1}
}

%% There is a package that you should include first: nag. Why first? Because it warns you about
%% obsolete commands and package. https://daniel-j-h.github.io/post/latex-a-modern-approach/
\usepackage[l2tabu,orthodox]{nag}

% Full submissions, submitted by the full paper submission deadline, should contain the abstract and the complete paper. The abstract should summarize the paper’s contributions. There is no page limit and authors are encouraged to use the “full version” of their paper as the submission. The submission should contain, within the initial ten pages following the title page, a clear presentation of the merits of the paper, including a discussion of the paper’s importance within the context of prior work and a description of the key technical and conceptual ideas used to achieve its main claims. The submission should be addressed to a broad spectrum of theoretical computer science researchers. Proofs must be provided which can enable the main mathematical claims of the paper to be fully verified. Although there is no bound on the length of a submission, material other than the abstract, references, and the first ten pages will be read at the committee’s discretion. Authors are encouraged to put the references at the very end of the submission. The submission should be typeset using 11-point or larger fonts, in a single-column, single-space (between lines) format with ample spacing throughout and 1-inch margins all around, on letter-size (8 1/2 x 11 inch) paper. Submissions deviating significantly from these guidelines risk rejection without consideration of their merits.

%% ANONYMOUS SUBMISSIONS

\usepackage{ifthen}
\newcommand{\anonymous}[2]{%
\ifthenelse{\equal{\isanonymous}{1}}%
{#1}%
{#2}%
}%

\newcommand{\fullversion}[2]{%
\ifthenelse{\equal{\isfullversion}{1}}%
{#1}%
{#2}%
}%

\newcommand{\submissionresizebox}[1]{
  \fullversion{
    #1
  }{
    \resizebox{.95\textwidth}{!}{#1}
  }
}

\fullversion{
    \usepackage{fullpage}
}{}

%% MARGINS

\fullversion{
  \usepackage[margin=1in]{geometry}
  \setlength{\marginparwidth}{1in}
  \setlength{\marginparsep}{0pt}
}{
  \usepackage[pass]{geometry}
}

%% MISC PACKAGES

\usepackage{microtype}
\usepackage[bookmarksdepth=2,backref]{hyperref}
\hypersetup{colorlinks=true,linkcolor={red!50!black},citecolor=darkgray,linkcolor=darkgray}
\usepackage{booktabs}  %% tables
\usepackage{comment}
\usepackage[inline]{enumitem}
\usepackage{nicematrix}
\usepackage{thm-restate}
\usepackage{tabularx}
\usepackage{breakcites}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[
    lambda,
    operators,
    advantage,
    sets,
    adversary,
    landau,
    probability,
    notions,
    logic,
    ff,
    mm,
    primitives,
    events,
    complexity,
    asymptotics,
    keys]{cryptocode}


\usepackage{ifluatex}
\ifluatex
\usepackage{luatex85}
\fi
% \usepackage{navigator} % Somehow incompatible?


\usepackage{amsthm}     	   	% Maths    
\newtheorem{definition}{Definition}                                      
\usepackage[utf8]{inputenc}	% UTF-8 characters                                               
\usepackage[T1]{fontenc}    	
% \usepackage{todonotes}
\usepackage{tcolorbox}

\usepackage{amsfonts,graphicx}


%% PDF SETUP

\pagestyle{plain}
\hypersetup{colorlinks=true,citecolor=darkgray,linkcolor=darkgray}
\allowdisplaybreaks

%% REFERENCES
\usepackage[capitalize]{cleveref}
\AddToHook{cmd/appendix/before}{\crefalias{section}{appendix}}
\AddToHook{cmd/appendix/before}{\crefalias{subsection}{appendix}}
\DeclareRobustCommand{\cshref}[1]{{\abbrevcrefs\cref{#1}}}

%% COMMENTS, BUGS, TODOS
\usepackage[draft]{comments-bugs-todos} % use "draft" option to show comments, bugs, todos

\input{macro}



\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{decorations.pathmorphing}


\definecolor{cgreen}{RGB}{0, 153, 51}
\definecolor{cblue}{RGB}{0, 102, 204}
\definecolor{cyellow}{RGB}{255, 204, 0} 
\definecolor{cred}{RGB}{204, 51, 0} 

\newtcolorbox{todobox}{colback=yellow!3!white, colframe=white!75!black}

\newcommand{\commentline}[2]{%
    \tikz[remember picture, overlay]{
        \node [black,anchor=west,xshift=10pt] at (#1) {#2};
    }
}

\newcommand{\blockcomment}[3]{%
    \tikz[remember picture, overlay]{
        \draw [decorate,decoration={lineto,amplitude=10pt,mirror,raise=4pt},yshift=0pt,very thick,{#3}] 
        (#1) -- (#2) node [black,midway,xshift=10pt] {};
    }
}

\begin{document}         
\author{Russell W. F. Lai \and Lorenzo Tucci}
\title{Ring Confidential Commit Transactions (RingCCT) for Private Atomic Swaps}

\maketitle

\tableofcontents
\newpage


\begin{todobox}
\textbf{Narrative}
\begin{itemize}
\item Universal atomic swaps allow atomic swaps across arbitrary pairs of chains which support ordinary transactions, in particular without requiring support of scripting, time-lock contracts, etc.
\item This is appealing because most privacy chains (e.g. ZCash, Monero, MimbleWimble) do not support scripting.
\item However, UAS requires both parties to solve TLPs, which are computationally intensive especially for lightweight clients.
\item Moreover, it is tricky from an implementation perspective to properly set the difficulty level TLPs in UAS. For example, we identify a minor flaw ... and propose a fix.
\end{itemize}

\textbf{Contributions}
\begin{itemize}
\item We identify that a minimal chain functionality -- commit transactions -- suffices for achieving atomic swaps. Concretely, we propose a generic construction of an atomic swap protocol using only commit transactions and other basic functionalities of the chains. (To avoid dealing with UC, maybe we write this as an informal theorem?)
\item We propose an extension of RingCT, the underlying transaction scheme of Monero, which allows to realise commit transactions in privacy-preserving cryptocurrencies. We propose a generic construction and show how to efficiently instantiate it over groups where discrete logarithm and other related problems are hard. 
\item We provide a prototype implementation of CommitTx-based atomic swaps
\end{itemize}
\end{todobox}

\input{intro}
\input{prelim}
\input{atomic_swap_overview}
\input{comm_tx}
\input{ringcct}
\input{experiments}

\bibliographystyle{alpha}
\bibliography{cryptobib/abbrev3,cryptobib/crypto,references}

\end{document}